\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-09-03 papers/methods/paper.tex
Paper updates

>>>>

\subsection{Uncertainty Analysis}
\label{sec:ucnert}

With the increased flexibility of Bayesian hierarchical models over traditional modes, we expect to find an increased uncertainty on parameter inference. To characterise the influence of the extra degrees of freedom in our model, we analyse the uncertainty on $w$ averaged across 10 nominal simulations of the DES three-year spectroscopic survey with various model parameters allowed to vary or locked to a fixed value. By taking the difference in uncertainty in quadrature, we can infer the relative contribution for each model feature to the uncertainty error budget.

\begin{table}
	\centering
	\caption{The error budget on $w$, as determined from analysing uncertainty on simulation data whilst progressively enabling model features.}
	\label{tab:uncert}
	\begin{tabular}{l|rr}
		Feature & $\sigma_w$ & Cumulative  \\
		\hline
		Cosmology only                 & 0.051  &   0.051       \\
		Standardisation parameters     & 0.046  &   0.068       \\
		Intrinsic scatter              & 0.020  &   0.071       \\
		Static survey populations      & 0.022  &   0.074       \\
		Redshift-dependent populations & 0.030  &   0.080       \\
		Systematics                    & 0.054  &   0.096       \\
		\hline
	\end{tabular}
\end{table}

The error budget detailed in Table \ref{tab:uncert} shows that our uncertainty is still dominated by statistical error, as the total statistical uncertainty is on $w$ is $0.08$. With the low number of supernovae in the DES three-year spectroscopic sample, this is expected. We note that the label `Systematics' in Table \ref{tab:uncert} represents all numerically computed systematics (as discussed in Section \ref{sec:systreat}) and systematic uncertainty on the selection function.

\subsection{Methodology Comparison}
\label{sec:comp}

{\red Introduce BBC. Highlight its use on Panstars}

{\red have plots for w-w comparison for g10 and c11}

{\red conclude that correlation is good, yay, have extra uncertainty, but this can be explained from previous section}
